---
title: "Homework 4"
output: 
 github_document:
  toc: TRUE
  df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(broom)
```

### Overview

The goal of homework 4 is to learn more about `map` functions from the `purrr` package.

### `Purrr`'s `map()` functions  

`Purrr` provides a set  of `map` functions (`map()`, `map_lgl()`, `map_chr()`, `map_int()`, `map_dbl()`, `map_raw()`, `map_df()`, `map_dfr()`, `map_dfc()`,  `walk()`) that allow you to apply a function to each element of a list or simple vector. 

These functions can be used to solve a variety of problems that require iteration. 

For example, below, I use `map()` to compute the correlation between the `mpg` variable and all the other variables in the `mtcars` dataset. 

```{r}
mtcars %>% 
	map(~cor.test(., mtcars$mpg)) %>% 
	map_df(tidy) %>% 
	mutate(name = names(mtcars))
```

### Your mission, high-level

Write a tutorial demonstrating  **two** different `map` functions. Use the `map` functions to solve a problem that interests you. 

Your tutorial should teach someone how to use your chosen `map()` functions. You can assume that person is in our course and knows as much *R* as we've covered thus far.

### The specifics

Teach someone how to use **two** of these functions: `map()`, `map_lgl()`, `map_chr()`, `map_int()`, `map_dbl()`, `map_raw()`, `map_dfr()`, `map_dfc()`, `map_if()`, `map_at()`,  `walk()`.

You will teach these `map` functions by demonstrating how they can be used to solve a problem. You get to pick the problem and the data you use. You can pick separate problems (one per `map` function) or could use two `map` functions in concert to solve a single problem (like I did above). 

Walk your reader through how the map function works. Take a look at the [RStudio primer](https://rstudio.cloud/learn/primers) on iteration if you need help explaining how to use the map functions. 

Compare the two `map` functions and describe when one type of `map` might be more useful than the other, and vice versa. 

### I want to do more!

`Purrr` has several advanced `map` functions (e.g., `map2()`, `pmap()`, `pwalk()`) that allow you to solve increasingly complex iteration problems. Pick one of these functions and demonstrate how it works. 

### What should I do?

#### Picking data

Remember that all data frames are lists, so you can use `map` to apply functions to any data frame we've covered in the course or a data set of your choosing. When mapping functions to data frames, you'll need to consider the data type of the columns. If you `map` `mean()` to a data frame of character vectors, you aren't going to have a happy time.

Your tutorial doesn't need to focus on data frames. For example, you might want to iterate over a vector of characters or numbers. 

#### Picking a problem

Try to make the tutorial useful for future you. What type of tasks do you commonly do in your research? Could they be streamlined with `purrr`?

At the end of the class on `purrr`, I showed you a few different ideas for problems you could solve with `purrr`, feel free to use those as inspiration. 

You might take a look at the [RStudio primer](https://rstudio.cloud/learn/primers) on iteration for ideas of problems to solve.

Finally, the problem you pick doesn't need to be complex. You simply need something that allows you to demonstrate your understanding of the `map` functions.

#### Ask for help

If you have trouble with this homework, please email me to ask for advice.

### Report your process

You're encouraged to reflect on what was hard/easy, problems you solved, helpful tutorials you read, etc. Give credit to your sources, whether it's a blog post, a fellow student, an online tutorial, etc.

### Rubric

As always, refer to the [general rubric](general-rubric.md) for guidelines on how we'll be grading.

Check minus: Reproduced something we covered in class or a very modest extension. The tutorial is difficult to understand. There is no obvious effort to explore the differences between the two `map()` functions you cover. Or more than one technical problem that is relatively easy to fix. It's hard to find the report in your Rproject folder

Check: Hits all the elements. No obvious mistakes. Pleasant to read. No heroic detective work is required. Solid.

Check plus: Exceeded the requirements in a number of tasks. Or developed novel approaches that were indeed interesting and "worked". Impressive use of `purrr` to meet the goals of the assignment. Thoughtful application of the `map` functions to solving your chosen problem. Impeccable organization of your report. We learned something new from reviewing your work and are eager to incorporate it into our work.

